---
title: "BGG Explorer Github"
author: "Michael Weisner"
date: "November 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r}
library(tidyverse)
library(ggplot2)
library(psych)
```
## BGG Data
```{r}
games <- read_csv(unzip("~/bgg_explorer/bgg_db_1806.csv.zip"))
```

## Quick Cleaning
I used this to quickly cut out some outliers, but they need closer examination!
```{r}
games_clean <- drop_na(games)
outliers <- subset(games_clean, max_players >32 | avg_time > 240 | min_time > 240 | max_time > 240)
games_clean <- subset(games_clean, max_players <=32 & avg_time <=240 & min_time <= 240 & max_time <= 480)

#head(games_clean)
summary(games_clean)
```

Look at Outliers if necessary
```{r}
#View(outliers)
```

## Cleaning

### Mechanics
https://boardgamegeek.com/browse/boardgamemechanic
Create dummy variables for mechanics?
Idea: do a for loop that goes through the mechanics vector and looks for the string matching that vector location across the Mechanics variable, and if so adding a 1 to a new mechanic for that column?

Maybe:
games$mechanic %>%
if(str_detect("Acting") {
mutate(Acting = 1)
} else{
Acting = 0
}
```{r}
mech_raw <- c("Acting","Action / Movement Programming", "Action Point Allowance System", 
               "Area Control / Area Influence", "Area Enclosure", "Area Movement", "Area-Impulse",
               "Auction/Bidding", "Betting/Wagering", "Campaign / Battle Card Driven", "Card Drafting",
               "Chit-Pull System", "Commodity Speculation", "Co-operative Play", "Crayon Rail System",
               "Deck / Pool Building", "Dice Rolling", "Grid Movement", "Hand Management", "Hex-and-Counter",
               "Line Drawing", "Memory", "Modular Board", "Paper-and-Pencil", "Partnerships", "Pattern Building",
               "Pattern Recognition", "Pick-up and Deliver", "Player Elimination", "Point to Point Movement",
               "Press Your Luck", "Rock-Paper-Scissors", "Role Playing", "Roll / Spin and Move", "Route/Network Building",
               "Secret Unit Deployment", "Set Collection", "Simulation", "Simultaneous Action Selection", "Singing",
               "Stock Holding", "Storytelling", "Take That", "Tile Placement", "Time Track", "Trading", "Trick-taking",
               "Variable Phase Order", "Variable Player Powers", "Voting", "Worker Placement")


# Add columns for each mechanic type
games[, mech_raw] <- 0

# Update values of dummy mechanics if present in games$mechanic
for(j in 1:length(mech_raw)){
  for(i in 1:length(games$mechanic)){
    games[i, as.character(mech_raw[j])] <- as.numeric(grepl(mech_raw[j], games$mechanic[i]))
  }
  cat("now at ", round(j * 1.96), "% ... ")
}

# head(games)
```

### Rename Mechanics
```{r}
# colnames(games)
testnames <- games[1:5, ]
colnames(testnames) <- tolower(colnames(testnames))
colnames(testnames) <- gsub("co-op", "coop", colnames(testnames)) # odd one out with dash
colnames(testnames) <- gsub("\\/", " ", colnames(testnames))
colnames(testnames) <- gsub("-", " ", colnames(testnames))
colnames(testnames) <- gsub(" and ", " ", colnames(testnames))
colnames(testnames) <- gsub("  ", " ", colnames(testnames))
colnames(testnames) <- gsub("  ", " ", colnames(testnames))
colnames(testnames) <- gsub(" ", "_", colnames(testnames))

```


### Categories
Do the same thing with categories
https://boardgamegeek.com/browse/boardgamecategory
Maybe figure out way to just comma separate them into a new data frame and then pull out unique values?
```{r}
cat_names <- as.data.frame(games$category)
cat_names <- extract(games, category, c("Type1", "Type2", "Type3", "Type4", "Type5", "Type6", "Type7"), sep = "([[:alnum:]]+),([[:alnum:]]+),([[:alnum:]]+),([[:alnum:]]+),([[:alnum:]]+),([[:alnum:]]+),([[:alnum:]]+)")
head(cat_names)
```

### Times
```{r}
describe(games_clean$avg_time)
```

### Num Players


## Quick LM
```{r}
lm1 <- lm(geek_rating ~ min_players + max_players + avg_time + age + weight + Acting + `Action / Movement Programming` + `Action Point Allowance System` + `Area Control / Area Influence` + `Area Enclosure` + `Area-Impulse` + `Auction/Bidding` + `Betting/Wagering` + `Campaign / Battle Card Driven` + `Card Drafting` + `Chit-Pull System` + `Commodity Speculation` + `Cooperative Play` + `Crayon Rail System` + `Deck / Pool Building` + `Dice Rolling` + `Grid Movement` + `Hand Management` + `Hex-and-Counter` + `Line Drawing` + Memory + `Modular Board` + `Paper-and-Pencil` + `Partnerships` + `Pattern Building` + `Pick-up and Deliver` + `Player Elimination` + `Point to Point Movement` + `Press Your Luck` + `Rock-Paper-Scissors` + `Roll / Spin and Move` + `Route/Network Building` + `Secret Unit Deployment` + `Set Collection` + `Simulation` + `Simultaneous Action Selection` + `Singing` + `Stock Holding` + `Storytelling` + `Take That` + `Tile Placement` + `Time Track` + Trading + `Trick-taking` + `Variable Phase Order` + `Variable Player Powers` + Voting + `Worker Placement`, data = games_clean)
summary(lm1)
```


## Plotting
```{r}
gg <- ggplot(data = games_clean, aes(x = geek_rating, y = owned, col = avg_time))
gg <- gg + geom_point()
gg <- gg + geom_smooth()
gg

```

